---
title: "Prison Break Report"
author: "Aleksander Partyga"
date: "6 04 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Prison Break

### Description
*[Prison Break](https://en.wikipedia.org/wiki/Prison_Break#References)* is an American serial drama television series created by *Paul Scheuring* for *Fox*. The series revolves around two brothers, *Lincoln Burrows* (*Dominic Purcell*) and *Michael Scofield* (*Wentworth Miller*); *Burrows* has been sentenced to death for a crime he did not commit, and *Scofield* devises an elaborate plan to help his brother escape prison and clear his name. Along with creator *Paul Scheuring*, the series is executive produced by *Matt Olmstead*, *Kevin Hooks*, *Marty Adelstein*, *Dawn Parouse*, *Neal H. Moritz*, and *Brett Ratner* who directed the pilot episode. The series' theme music, composed by *Ramin Djawadi*, was nominated for a *Primetime Emmy Award* in 2006.[1] *Prison Break* is a joint production between *Original Film*, *Adelstein/Parouse Productions* (seasons 1-4), *Dawn Olmstead Productions* (season 5), *Adelstein Productions* (season 5), *One Light Road Productions* (season 5) *and 20th Century Fox Television*, and is syndicated by *20th Television*.

```{r}

```