---
title: "Prison Break Report"
author: "Aleksander Partyga"
date: "6 04 2022"
output: html_document
---

```{r setup, include=FALSE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Prison Break

### 1. Description
*[Prison Break](https://en.wikipedia.org/wiki/Prison_Break#References)* is an American serial drama television series created by *Paul Scheuring* for *Fox*. The series revolves around two brothers, *Lincoln Burrows* (*Dominic Purcell*) and *Michael Scofield* (*Wentworth Miller*); *Burrows* has been sentenced to death for a crime he did not commit, and *Scofield* devises an elaborate plan to help his brother escape prison and clear his name. Along with creator *Paul Scheuring*, the series is executive produced by *Matt Olmstead*, *Kevin Hooks*, *Marty Adelstein*, *Dawn Parouse*, *Neal H. Moritz*, and *Brett Ratner* who directed the pilot episode. The series' theme music, composed by *Ramin Djawadi*, was nominated for a *Primetime Emmy Award* in 2006.[1] *Prison Break* is a joint production between *Original Film*, *Adelstein/Parouse Productions* (seasons 1-4), *Dawn Olmstead Productions* (season 5), *Adelstein Productions* (season 5), *One Light Road Productions* (season 5) *and 20th Century Fox Television*, and is syndicated by *20th Television*.


```{r, echo=FALSE, warning = FALSE, message = FALSE}
# Define variable containing url
url <- "https://upload.wikimedia.org/wikipedia/en/d/d3/Prison-break-s1-intro.jpg"
```
### 2. Photo from the TV Series
<center><img src="`r url`"></center>

&nbsp;

### 3. Summarizing Prison Break viewership


```{r, echo = FALSE, warning = FALSE, message = FALSE}
season <- c(1, 2, 3, 4, 5)
viewers <- c(9.2, 9.3, 8.2, 6.1, 4.0)
rank <- c(55, 51, 73, 68, 115)

df <- data.frame(season, viewers, rank)
summary(df)
```

&nbsp;

### 4. A graph of the viewership over time


```{r, echo=FALSE, warning = FALSE, message = FALSE}
library(ggplot2)
ggplot(df, aes(x = season, y = viewers)) +
  geom_bar(stat = 'identity') +
  ggtitle('Number of viewers in each season of the Prison Break TV series') +
  ylab("Number of viewers (in million)") +
  xlab("Season")
```
&nbsp;

### 5. A graph of the ranking over time

```{r, echo=FALSE, warning = FALSE, message = FALSE}
library(tidyverse)
ggplot(df, aes(x = season, y = reorder(rank, desc(rank)), group = 1)) +
  geom_line(linetype = 'dashed', color = 'blue') +
  geom_point() +
  ggtitle('Place in the popularity ranking by season') +
  ylab("Place in the ranking") +
  xlab("Season")
```




